Notes on Perturbational Quantities

### 2008-07-29 docs/pert_notes/paper.tex
more updates of rho section

Full density evolution equation:
\frac{\partial\rho}{\partial t} &=& -\nabla\cdot(\rho\Ub) \nonumber \\
&=& -\Ub\cdot\nabla\rho -\rho\nabla\cdot\Ub. \label{rho equation}

@@

Base state density evolution equation:
\frac{\partial\rho_0}{\partial t} &=& -\nabla\cdot(\rho_0 w_0 \eb_r) - 
\nabla\cdot(\eta_\rho \eb_r) \nonumber \\
&=& -w_0\frac{\partial\rho_0}{\partial r} \underbrace{- 
\rho_0\frac{\partial w_0}{\partial r}} 
- \nabla\cdot(\eta_\rho \eb_r). \label{rho0 equation}
Note that $\Ub = \Ubt + w_o\eb_r$.  Subtract (\ref{rho0 equation}) from 
(\ref{rho equation}) to give perturbational density equation:
\frac{\partial\rho'}{\partial t} &=& -\nabla\cdot(\rho'\Ub) - \nabla\cdot(\rho_0\Ubt) 
+ \nabla\cdot(\eta_\rho \eb_r) \nonumber \\
&=& -\Ub\cdot\nabla\rho' \underbrace{- \rho'\nabla\cdot\Ub - \nabla\cdot(\rho_0\Ubt)} 
+ \nabla\cdot(\eta_\rho \eb_r).\label{rho' equation}

@@

term in (\ref{rho' equation}) is computed in modify\_scal\_force.  The $\eta_\rho$ term 
is not included, but this is correct because the procedure to compute $\rho$ at edges 
described in Section \ref{Computing rho at edges} makes use of an edge-centered, 
time-centered $\rho_0^{n+\half}$ that does not include an $\eta_\rho$ contribution either.

@@

We first compute $\rho_0^{(2)}$ using advect\_base (but not correct\_base).  We compute 
$\rho$ on edges by adding $\rho_0^{n+\half} = (\rho_0^n + \rho_0^{(2)}) / 2$ to $\rho'$ at 
edges. For the non-radial faces, we can directly add $\rho_0^{n+\half}$ since it is a 
cell-centered quantity.  For the radial faces, we interpolate to obtain $\rho_0^{n+\half}$ 
at radial faces.

@@

is set to zero, and therefore we set is\_conservative = T to alter the discretization 
in make\_edge\_scal.

@@

underbraced term in (\ref{rho0 equation}) as the forcing.  The $\eta_\rho$ term is not 

@@

&=& -\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub -\nabla\cdot(\rho h \Ub) 
+ \frac{Dp_0}{Dt} + \nabla\cdot\kappa\nabla T + \rho H_{\rm nuc} 
+ \rho H_{\rm ext}.\label{rhoh equation}

>>>>

The full density evolution equation is
\frac{\partial\rho}{\partial t} = -\nabla\cdot(\rho\Ub) = -\Ub\cdot\nabla\rho 
- \rho\nabla\cdot\Ub. \label{rho equation}

@@

The base state density evolution equation is
\frac{\partial\rho_0}{\partial t} = -\nabla\cdot(\rho_0 w_0 \eb_r) = 
-w_0\frac{\partial\rho_0}{\partial r} - \rho_0\frac{\partial w_0}{\partial r}.
\label{rho0 equation}
Subtract (\ref{rho0 equation}) from (\ref{rho equation}) and rearrange, noting that 
$\Ub = \Ubt + w_o\eb_r$, to obtain the perturbational density equation,
\frac{\partial\rho'}{\partial t} = -\Ub\cdot\nabla\rho' \underbrace{- \rho'\nabla\cdot\Ub 
- \nabla\cdot(\rho_0\Ubt)}_{"\rho' ~ \text{force}"}. 
\label{rhoprime equation}

@@

forcing term in (\ref{rhoprime equation}) is computed in modify\_scal\_force.

@@

We first compute $\rho_0^{(2)}$ from $\rho^n$ using advect\_base.  The $(2)$ in the 
superscript indicates that we have not called correct\_base yet.  We compute $\rho$ on edges 
by adding $\rho_0^{n+\half} = (\rho_0^n + \rho_0^{(2)}) / 2$ to $\rho'$ at edges.  We use 
$\rho^{(2)}$ rather than $\rho^{n+1}$ to be consistent with the fact that we omitted the 
$\eta_\rho$ contribution to $\rho'$ at edges.  For the non-radial faces, we can directly add 
$\rho_0^{n+\half}$ to $\rho'$ since it is a cell-centered quantity.  For the radial faces, we 
interpolate to obtain $\rho_0^{n+\half}$ at edges.

@@

is set to zero, but then we set is\_conservative = T to use the conservative 
discretization in make\_edge\_scal.

@@

term proportional to $\rho_0$ in  (\ref{rho0 equation}) as the forcing.  The $\eta_\rho$ 
term is not 

@@

&=& \underbrace{-\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub}_{-\nabla\cdot(\rho h\Ub)} 
+ \underbrace{\psi + \Ubt\cdot\nabla p_0}_{\frac{Dp_0}{Dt}} + \nabla\cdot\kappa\nabla T 
+ \rho H_{\rm nuc} + \rho H_{\rm ext}\label{rhoh equation}
